Facility and Time Step Discretization Effects in Fuel Cycle Simulation

### 2015-09-21 paper.tex
fix bullets from dissertation context to paper context

    \item How well do fleet-based models with continuous material flow capture
    optimal fuel cycle transitions compared to individual facility modeling?

    \item What effects are the primary drivers for differences in fleet-based
    and individual-based facility modeling?

    \item Does the impact of time step duration changes differ in fleet-based
    and individual-based facility modeling?

>>>>

    \item What effects drive differences in fleet-based and individual-based
        facility modeling?

    \item How does changing the time step duration affect simulations?

    \item Does the impact of changing time step duration differ in fleet-based
        and individual-based facility modeling?
